Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-09 minimax.tex
Fixing floats
Saving a bit more space, reduced to 8 pages

\subsection{Relative evaluation of Pessimistic strategy}
\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{comparison.png}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
\end{figure}
\begin{table}
	\begin{center}
			\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
				\toprule
				{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
				\midrule
				0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
				50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
				100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
				150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
				200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
				250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
				300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
				350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
				400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
				\bottomrule
			\end{tabular}
	\end{center}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
\end{table}
\begin{table}
	\begin{center}
			\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
				\toprule
				{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
				\midrule
				0	&20.0	&0.0	&20.0	&0.0\\
				100	&12.48	&0.93	&15.6	&0.43\\
				200	&7.43	&1.25	&10.95	&1.12\\
				300	&3.47	&1.32	&6.57	&0.79\\
				\bottomrule
			\end{tabular}
	\end{center}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
\end{table}

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  55 \\
			5 & 15 & 1.5 & 80 &  83 \\
			5 & 20 & 2.0 & 110 &  110 \\
			10 & 20 & 2.0 & 340 &  341 \\
			10 & 30 & 3.0 & 527 &  512 \\
			15 & 30 & 3.0 & 812 &  991 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
	\label{tab:lowRegret}
\end{table}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
			\toprule
			m & k \\
			\midrule
			5 & 6.6\\
			10 & 24.8\\
			15 & 48.4\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
	\label{tab:fullProfile}
\end{table}

@@

\subsection{Decrease in MMR values}
\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average MMR after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

@@

\subsection{Value of information comparison}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			15 & 0.71 & 0.73 & 0.67	& 0.64 \\
			30 & 0.62 & 0.5 & 0.8 & 0.62 \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 & 1.88 & 1.02  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 & 4.61	& 1.35  & 6.53 & 2.0  \\
			250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
			300 &11.07 & 0.86& 11.87 & 1.25 \\
			350 &15.06 & 0.68&15.59 & 0.6 \\
			400 &20.0 & 0.0 & 20.0 & 20.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
	\label{tab:twoP400}
\end{table}

@@

These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis: when $p = 0$, no question is asked to the chair, and a good-quality recommendation is still reached after a relatively small number of questions. By contrast, the Pessimistic strategy, when unconstrained, asks X questions to the chair.

\section{Conclusions}  
\label{sec:conclusions}
%TODO balance columns appropriately before submitting
%\balance
In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
Our experimental results %on randomly generated and real world data sets 
suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly. They also highlight the importance of not insisting to obtain a completely specified voting rule, as good quality (low regret) recommendations can be achieved short of knowing the weights precisely, in our setting.
%regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem. Future works will therefore include the test of these strategies on partial specified profiles, ideally on real datasets. An other important direction is the extension to voting rules beyond scoring rules.
%Regret-based elicitation allows to determine near-optimal winners using only few information about the agent preferences.

>>>>

\subsection{Relative evaluation of Pessimistic strategy}
\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
	\includegraphics[width=.45\textwidth]{comparison.png}
\end{figure}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		100	&12.48	&0.93	&15.6	&0.43\\
		200	&7.43	&1.25	&10.95	&1.12\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
	\label{tab:lowRegret}
	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
		\toprule
		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
		\midrule
		5 & 10 & 1.0 & 60 &  55 \\
		5 & 15 & 1.5 & 80 &  83 \\
		5 & 20 & 2.0 & 110 &  110 \\
		10 & 20 & 2.0 & 340 &  341 \\
		10 & 30 & 3.0 & 527 &  512 \\
		15 & 30 & 3.0 & 812 &  991 \\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
	\label{tab:fullProfile}
	\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
		\toprule
		m & k \\
		\midrule
		5 & 6.6\\
		10 & 24.8\\
		15 & 48.4\\
		\bottomrule
	\end{tabular}
\end{table}

@@

\subsection{Decrease in MMR values}
%TODO balance columns appropriately before submitting
\balance
\begin{figure}
	\caption{Average MMR after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
	\includegraphics[width=.45\textwidth]{linearity.png}
\end{figure}

@@

\subsection{Value of information comparison}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
	\label{tab:twoP400}
	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
		\midrule
		0 & 0.66 & 0.67 & 0.65 & 0.65  \\
		15 & 0.71 & 0.73 & 0.67	& 0.64 \\
		30 & 0.62 & 0.5 & 0.8 & 0.62 \\
		50 & 1.23 & 1.46 & 0.8 & 0.79 \\
		100 & 2.03 & 1.56 & 1.88 & 1.02  \\
		150 & 3.41 & 1.79 & 4.07 & 1.51 \\
		200 & 4.61	& 1.35  & 6.53 & 2.0  \\
		250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
		300 &11.07 & 0.86& 11.87 & 1.25 \\
		350 &15.06 & 0.68&15.59 & 0.6 \\
		400 &20.0 & 0.0 & 20.0 & 20.0 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

These numbers highlight that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule and that the weights are convex, which is our basic hypothesis (corresponding to the line $q_c = 0$, where no question is asked to the chair). By contrast, the Pessimistic strategy, when unconstrained, asks X questions to the chair.

\section{Conclusions}  
\label{sec:conclusions}
In this paper we have considered a social choice setting with partial information about the agent's preferences and a partially specified voting rule.
In this setting, we have proposed the use of minimax regret both as a means of robust winner determination as well as a guide to the process of simultaneous elicitation of preferences and voting rule.
Our experimental results %on randomly generated and real world data sets 
suggest that regret-based elicitation is effective and allow to quickly reduce worst regret significantly. They also show that good quality (low regret) recommendations can be achieved short of knowing the weights precisely or the profile completely, in our setting.
%regret, but they also show that starting with zero knowledge became a pretentious approach really quickly when increasing the size of the problem. Future works will therefore include the test of these strategies on partial specified profiles, ideally on real datasets. An other important direction is the extension to voting rules beyond scoring rules.
%Regret-based elicitation allows to determine near-optimal winners using only few information about the agent preferences.
